---
title: "Stroop"
output: html_document
date: "2024-02-28"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Stroop Data Analysis

**Research Question:**

* Is there a cost of interference on the speed of processing?

**Hypothesis:**

* Responses in incongruent trials, where the word and ink color do not match, will be slower than responses for congruent tri

Define some pretty colors

```{r}
colours <- hcl.colors(3, palette = "Zissou 1")
```

Load the data 

```{r}
stroopData <- read.csv("~/Downloads/StroopData.RData")
```

```{r}
str(stroopData)
```

## Quality Assurance

Get an overview of your data

* Missing Values
* Impossible Values
* Number of participants
* Number of congruent and incongruent trials
* Incorrect trials

## Exploratory Data Analysis

Explore the distribution of interesting or relevant variables

* Identify your outcome variable
* Determine the central tendency of your outcome variable
* Obtain a point estimate of the difference in the central tendency of your outcome across groups

```{r}

```


## Analysis

Use a permutation test to determine the statistical significance of the difference in response time between congruent and incongruent trials

The permutation test procedure is as follows:

* Combine the results from the different groups into a single data set
* Shuffle the combined data and then randomly draw (without replacement) a resample of the same size as group A
  + Sampling with replacement is a bootstrap permutation test
* From the remaining data, draw (without replacement) a resample of the same size as group B
  + Repeat if more groups
* Calculate the same statistic you calculated for the original sample
* Repeat these steps N times to yield a permutation distribution of the test statistic

```{r}

```

## t-tests
H0 : Ni difference between response times for congruent and incongruent trials
H1: RT for incongruent trails are slower than congruent trials

RTDifference = incongruent - congruent <- one tail test

1 tail test 

##Assumptions of t test
1. Scale of Measurement
2. Random Sampling
3. Normality
4. Large Sample
5. Homogeneity of variance

```{r}

```

###Normality
```{r}
qqnorm(stroopData1$RT[stroopData.Clean$Word.Color.Relationship == "Congruent"])
qqline("")

qqnorm(stroopData1$RT[stroopData.Clean$Word.Color.Relationship == "Incongruent"])
qqline("")
```


```{r}
shapiro.test(log(stroopData.Clean1$RT[stroopData.Clean1$Word.Color.Relationship == "Congruent"]))

shapiro.test(log(stroopData.Clean1$RT[stroopData.Clean1$Word.Color.Relationship == "Incongruent"]))
```


##Homogenity of Variance
```{r}
car::leveneTest(stroopData.Clean1$RT,as.factor(stroopData.Clean1$Word.Color.Relationship))
```

### t-test

```{r}
dim(stroopData.Clean1)
dim(stroopData)

xtabs(~ ParticipantID + Word.Color.Relationship, data = stroopData.Clean1)
```


```{r}
t.test(log(RT) ~ Word.Color Relationship, data = stroopData.Clean1, alernative = "less", var.equal = TRUE, paired = TRUE)
```

```{r}
load("~/Downloads/StroopDataSubSampled.RData")
```

```{r}
xtabs(~ ParticipantID + Word.Color.Relationship, data = subSampledStroop)
```

```{r}
t.test(log(subSampledStroop$RT[subSampledStroop$Word.Color.Relationship == "Congruent"]) ~ Word.Color Relationship, data = stroopData.Clean1, alernative = "less", var.equal = TRUE)
```


##t-test by hand 

```{r}
subSampledStroop$RTlog <- log(subSampledStroop$RT)
```


```{r}
tapply(log(subSampledStroop$RT), subSampledStroop$Word.Color.Relationship, FUN = mean)
mDiff <- theMeans[2] - theMeans[1]

cov12 <- cor(subSampledStroop$RT[subSampledStroop$Word.Color.Relationship == "Congruent"], subSampledStroop$RT[subSampledStroop$Word.Color.Relationship == "Incongruent"]) * sd(subSampledStroop$RT[subSampledStroop$Word.Color.Relationship == "Congruent"]) * sd(subSampledStroop$RT[subSampledStroop$Word.Color.Relationship == "Incongruent"])

sdMeanDiff <- sqrt(var(subSampledStroop$RT[subSampledStroop$Word.Color.Relationship == "Congruent"]) + var(subSampledStroop$RT[subSampledStroop$Word.Color.Relationship == "Incongruent"])-(2*cov12)


seMeanDiff <- sdMeanDiff/sqrt(10)                   
                   
tCalculate <- mDiff/seMeanDiff
```






